---
title       : Car vs Car
subtitle    : Developing Data Products Course Project
author      : Ven Reddy
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---
## Introduction

This is an application that loads Motor Trend's Car Data (mtcars) and allows
a person to compare two cars against each other using the UI rather
than a command line.


```{r, echo=FALSE}
library(dplyr)
data(mtcars)
mtcars$names <- rownames(mtcars)
head(mtcars)
```

--- .class #id 
## Side panel 

The side panel allows you to pick two cars, an attribute to plot.  Click on 
the Submit button to have the application show you the comparison of both cars.

--- .class #id
## Main panel

The main panel shows you what cars that you have selected and also shows
the various attributes for each car such as mpg, cylinders, horsepower, etc.

For example:

```{r}
# show two cars
data(mtcars)
mtcars$names <- rownames(mtcars)
f <- c("Datsun 710", "Valiant")
filter(mtcars, names %in% f)

```


--- .class #id
## Thank you

Thank you for using this application.  I am sure that you will agree that
for the non-R programmer this is a much easier way of comparing two cars
against each other.